Variational Approximations for Transfer in Reinforcement Learning

### 2018-05-14 NIPS 2018/main.tex
appendix C

that is easily differentiable with respect to $\bm{\xi} = (\bm{\mu}_1,..., \bm{\mu}_C, \bm{\Sigma}_1,..., \bm{\Sigma}_C)$ using the Eq. \ref{eq:klgradmu}, \ref{eq:klgradL}, \ref{eq:tdgradmu}, \ref{eq:tdgradL}.

@@

@@

>>>>

that is easily differentiable with respect to $\bm{\xi} = (\bm{\mu}_1,..., \bm{\mu}_C, \bm{\Sigma}_1,..., \bm{\Sigma}_C)$ using the Eq. \ref{eq:klgradmu}, \ref{eq:klgradL}, \ref{eq:tdgradmu}, \ref{eq:tdgradL} derived for the Gaussian case.

@@

In the present section we present the hyper-parameters and corresponding values that were used for the experiments presented in this paper.

For all the algorithms implemented for the empirical evaluation, we used a Replay Buffer ($Buffer\_size$) with a fixed size and batches of a given size ($Batch\_size$) sampled randomly from it to perform the gradient steps.

In the case of no-transfer-based algorithms we used a linearly scheduled $\epsilon$-greedy exploration for which we could specify the starting and final values of $\epsilon$, $\epsilon_s$ and $\epsilon_f$ respectively, and the \emph{Exploration Fraction} of the maximum number of iterations for which the linear schedule would be used. As the learning procedure is done by gradient descent, we also have $\alpha$ as the learning rate. Additionally, in the case of the DDQNs we have the \emph{Target Update Frequency} that specifies the number of iterations before setting the target neural network to the current parameters of the online network.

As presented in Sec. \ref{sec:td}, for the minimization procedure of the TD error based on \emph{mellow-max} we also have to set $\kappa$ to control the approximation to the maximum operator and $\psi \in \left[0,1\right]$ to control the proportion between the full residual gradient and the semi-gradient approach used.

For the transfer algorithms proposed here, namely, GVT and MGVT we have the following parameters. As presented in Sec. \ref{sec:alg}, we have $\lambda \geq 0$ to control the trade-off between the prior knowledge and the loss measure---i.e. the TD error---in the target task. Moreover, we allow to control the learning rates differently for the gradients related to the means and covariance matrices, the Cholesky factor L to be precise: $\alpha_{\mu}$ and $\alpha_L$. In order to approximate the expectation of the TD error, we used a fixed number of $weights$ sampled from the posterior distribution. Specifically, for MGVT it is necessary to specify the value of the variance $\sigma_p^2$ for the prior model and the number of components $C$ for the posterior family to be used. Furthermore, as explained in Sec. \ref{sec:mgvt}, to perform the initialization of the posterior by minimizing the KL divergence we set the a maximum number of iterations (\emph{UKL max iterations}) and the precision to reach during this optimization $\varepsilon$ and its learning rate $\eta$. Finally, to avoid problems with the positive-definiteness of the covariances being learned, we specify a hyper-parameter $\sigma_{min}$ as the minimum value the diagonal elements of the Cholesky factor can reach.

In the following sections we present the configurations used for the experiments presented in this paper. For all our experiments we set $\psi=0.5$, $UKL\_max\_iterations=600$, $\eta=10^{-6}$, $\varepsilon=0.001$, $\sigma_{min}=0.0001$. Also, we used ADAM optimizer---with parameters $\beta_1=0.9$, $\beta_2=0.999$---for the gradients steps related to the means and simple SGD for gradients steps of the Cholesky factors L in GVT and MGVT. For the non-transfer algorithms only ADAM was used with the same mentioned parameters.

@@

For the Cartpole environment, we generated tasks by uniformly sampling the cart mass in the range $\left[0.5,1.5\right]$, the pole mass in $\left[0.1,0.3\right]$ and the pole length in $\left[0.2,1.0\right]$.

During the training of the source tasks, we used a $Batch\_size = 32$, $Buffer\_size = 50000$. For DDQN with a $Target\_Update\_Frequency = 500$ and $Exploration\_fraction = 0.35$ with $\epsilon_s=1$ and $\epsilon_f=0.1$. The function approximator was a Multilayer Perceptron (MLP) with ReLU as activation function and a hidden layer of $32$ neurons. For the transfer experiments we set $Batch\_size=500$ and $weights=5$, $\lambda=0.001$, $\alpha_{\mu}=0.001$ and $\alpha_L=0.0001$. In the case of MGVT we set $\sigma_p^2=10^{-5}$.

In the case of Mountain Car, to generate tasks we sampled uniformly the base speed of the actions in the range $\left[0.001, 0.0015\right]$. We trained DDQN with $Target\_Update\_Frequency = 500$ and $Exploration\_fraction = 0.15$ with $\epsilon_s=1$ and $\epsilon_f=0.1$ and used  an MLP with single hidden layer of $64$ neurons with ReLU activation. For the transfer experiments we set the $Batch\_size=50$, $weights=10$, $\lambda=10^{-5}$, $\alpha_{\mu}=0.001$ and $\alpha_L=0.0001$. For MGVT we set $\sigma_p^2=10^{-5}$.
